COG-ED Manuscript

### 2021-08-20 06_Paper/COG-ED/Manuscript.Rmd
cleaned questionnaire data and added computation of hypothesis 3a

@@

#auc(data_SV$level[1:4], data_SV$sv[1:4], method = "trapezoid", sort = FALSE) ->> gives you 2.23, which can't be

# for each participant subjective values for 1-, 2-, 3-, and 4-back will be calculated
# an area under the curve (AUC) will be calculated per participant
# regression
```

>>>>

  # remove unnecessary variables from questionnaire data frame

  data_quest <- subset(data_quest, select = -c(vl, date, preparatory_coged_complete, general_questions_timestamp, state,
                                               general_questions_complete, inclusion, inclusion_0___1, inclusion_0___2, inclusion_0_2,
                                               researcher_questions_complete, nasatlx_timestamp, nasatlx_complete, t1_psychopy_ed_csv,
                                               t1_psychopy_ed_psydat, t1_psychopy_nback_csv, t1_psychopy_log, t1_psychopy_nback_psydat,
                                               t1_psychopy_randch_log, t1_psychopy_randch_psydat, files_coged_complete, record_id_2, vl_er,
                                               date_er, humid_bef_er, preparatory_ered_complete, emg_eeg, emg_vhdr, emg_vmrk,
                                               er_ed_psychopy_txt, er_ed_psychopy_psydat, files_ered_complete, followup_ered_timestamp,
                                               nachb_01, nachb_01_inhalt, nachb_02, nachb_02_inhalt, nachb_03, nachb_07, nachb_07_inhalt,
                                               nachb_08, nachb_08_inhalt, nachb_08_haeufig, nachb_08_zurueck, followup_ered_complete,
                                               nfc_timestamp, nfc_complete, bis_11_timestamp, bis_11_complete, bscs_timestamp,
                                               bscs_complete, srs_timestamp, srs_complete, erq_erqse_timestamp, erq_erqse_complete,
                                               who5_timestamp, who5_complete, acs_timestamp, acs_complete, cdrisc_timestamp,
                                               cdrisc_complete, flexer_timestamp, flexer_complete))

@@

  # create an index for the rows in which the participants change

  subjectindex <- c(1,which(data_SV$subject != dplyr::lag(data_SV$subject)),nrow(data_SV))

  # prepare empty data frame for the loop to feed into

  data_hyp3 <- data.frame(subject = character(), auc = double())

  # calculate AUC of SVs per subject

    newdata <- data.frame(subject = data_SV$subject[subjectindex[i]],
                         auc = auc(data_SV$level[subjectindex[i]:(subjectindex[i+1]-1)], data_SV$sv[subjectindex[i]:(subjectindex[i+1]-1)],
                                   method = "trapezoid", sort = FALSE))
    data_hyp3 <- rbind(data_hyp3, newdata)

  # prepare temporary data frame for loop to feed into

  data_nfc <- data.frame(subject = character(), nfc = double())

  # calculate NFC scores for every subject

    nfc <- data_quest[setindex[i] + 2, grep("nfc", colnames(data_quest))]
    nfc[ ,c(4,6,7,8,9,10,11,12,15,16)] <-  nfc[ ,c(4,6,7,8,9,10,11,12,15,16)] * -1

    data_nfc <- rbind(data_nfc, data.frame(subject = data_quest$subject[setindex[i]],
                                           nfc = sum(nfc)))
  }

  # merge the NFC data frame into the AUC data frame by row

  data_hyp3 <- merge(data_hyp3, data_nfc)

  # delete temporary variables

  remove(nfc, data_nfc)

  # calculate linear model to estimate prediction of NFC by SVs

  hypothesis3a <- summary(lm(data_hyp3$nfc ~ data_hyp3$auc))
